### 2011-09-18 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress

TODO link BasicIGG to see how we get IG

TODO describe how we get the model

@@

\subsection{Measuring the time}

@@

\subsection{Obtaining the results}

Every run of an experiment produces a trace such as the one presented and commented on in Appendix \ref{appendix-trace}. We can get all the information relevant to that experiment run from this trace alone. An experimental set will produce a number of these traces and store them in plain text files in a folder. Parsing these files to aggregate and collate them might be a tedious task even using tools like \texttt{sed} and \texttt{grep}, so some of the experiment sets directly output tabular data in format recognized by GnuPlot, which we use to plot charts found in this work.

TODO explain boxplots, how to read them

>>>>

This section will briefly describe the process by which an input data set is processed to obtain the AM model as described in TODO link.\\

An input data set is essentialy a single XML file on the filesystem, however there is a straightforward extension to multiple files conforming to the same schema. The first step in this process is to use jInfer's module \jmodule{BasicIGG} module (see \cite{basiciggdoc} for details) to obtain a list of rules - an \textit{initial grammar} (IG). \nomenclature{IG}{Initial Grammar}
Please see \cite{archdoc} for detailed specification of IG format.\\

The second step is to convert the grammar into the AM model. This is done by scanning it in a linear fashion and retrieving a so-called \textit{flat} representation. This consists of a list of tuples in the following format.

\begin{center}
\textit{(element name, attribute name, attribute value)}
\end{center}

There is a tuple for every attribute node with a value found in the initial grammar. Note that the information about the context in which the element was originally found is lost - but this is not a problem with regard to the definition of XML ID attributes. Furthermore, tuples in flat representation do not need to be unique.\\

The model now has to be able to return the list of all attribute mappings and their respective images. This is achieved by simply grouping the flat representation by the pair \textit{(element name, attribute name)} and aggregating all attribute values for each such pair. Another responsibility of the model is to return the list of \textit{types} - that is simply the list of unique \textit{element name}s.

\subsubsection{Example}

This example will present the whole process, from an input XML file to the model and its AMs and types.

Consider the following XML file fragment.
\begin{verbatim}
<x>
  <y a="1" b="2"/>
  <y a="3" c="4"/>
  <y/>
  <z a="1"/>
</x>
\end{verbatim}

Its IG representation is the following set of IG rules.

\begin{eqnarray*}
	x & \to & y, y, y, z \\
	y & \to & @a, @b \\
	y & \to & @a, @c \\
	y & \to & empty\_concatenation \\
	z & \to & @a \\
\end{eqnarray*}

The flat representation will consist of the following set of tuples.

\begin{eqnarray*}
(y, a, 1) \\
(y, b, 2) \\
(y, a, 3) \\
(y, c, 4) \\
(z, a, 1) \\
\end{eqnarray*}

Attribute mappings in this model will be $(y, a)$, $(y, b)$, $(y,c)$ and $(z,a)$. Their images will be $(1,3)$, $(2)$, $(4)$ and $(1)$, respectively. The list of types in this model will be $(y,z)$.

@@

\subsection{Measuring the Time}

@@

\subsection{Obtaining the Results}

Every run of an experiment produces a trace such as the one presented and commented on in Appendix \ref{appendix-trace}. We can get all the information relevant to that experiment run from this trace alone. An experimental set will produce a number of these traces and store them in plain text files in a folder. Parsing these files to aggregate and collate them might be a tedious task even using tools like \texttt{sed} and \texttt{grep}, so some of the experiment sets directly output tabular data in format recognized by GnuPlot \cite{gnuplot}, which we use to plot charts found in this work.

\subsection{Reading Boxplots}

To present a set of measurements obtained by iteratively running an experiment we shall prominently use the \textit{boxplot} chart. Because we use boxplots produced by GnuPlot, let us quote its manual (\cite{gnuplot-manual}) for the exact definition.

\begin{quote}
Quartile boundaries are determined such that 1/4 of the points have a value equal or less than the first quartile boundary, 1/2 of the points have a value equal or less than the second quartile (median) value, etc. A box is drawn around the region between the first and third quartiles, with a horizontal line at the median value. Whiskers extend from the box to user-specified limits. Points that lie outside these limits are drawn individually.
\end{quote}

The ``user-specified limits" of whiskers are set to default value, let us quote again from the manual.

\begin{quote}
By default the whiskers extend from the ends of the box to the most distant point whose y value lies within 1.5 times the interquartile range.
\end{quote}
